Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-02-14 ms.tex
Should be en-dash

The marginalization over $D_\mathrm{L}$, $x$, and $\psi$ must be done numerically. The outermost integration is over x and $\psi$, and is done with Newton-Cotes by evaluating $\mathcal{L}_\mathrm{SNR}$ on a regular lattice in $x$ and $\psi$. This integration scheme is first order in $x$ and second order in $\psi$.

>>>>

The marginalization over $D_\mathrm{L}$, $x$, and $\psi$ must be done numerically. The outermost integration is over x and $\psi$, and is done with Newton--Cotes by evaluating $\mathcal{L}_\mathrm{SNR}$ on a regular lattice in $x$ and $\psi$. This integration scheme is first order in $x$ and second order in $\psi$.
